Current State of Knowledge Representation Systems for Robotics

### 2011-11-21 paper.tex
Added notes on PEIS Ecology. Prbl: no KRS...?

\begin{tabularx}{\textwidth}{llp{2cm}p{4cm}p{2.3cm}p{2cm}p{2cm}}
\hiderowcolors
{\bf Name} & {\bf Authors (Institution)} & {\bf Surveyed version} & {\bf Project homepage} & {\bf Programming language} & {\bf Knowledge model} & {\bf Reasoner} \\
\hline
\showrowcolors
{\sc KnowRob} & Tenorth (TU Munich) & & & {\sc Prolog} & {\sc Prolog} + OWL-DL & Custom ({\sc Prolog}) \\
ORO & Lemaignan (LAAS-CNRS) & 0.8.0 & \url{oro.openrobots.org} & {\sc Java} & OWL-DL ({\sc Jena}) & {\sc Pellet} \\
PEIS Ecology & Saffiotti, Coradeschi \\
 & Kollar, Tellex \\
OMKRF \\
 & Roy, Mavridis \\
 & Wrighteagle \\
 & Vincze \\
 & (Bielfeld) \\
ARMAR & Schmidt-Rohr (Karlsruhe) \\
 & (Saarbrücken) \\
 & Hertzberg (Osnabrück) \\
 & (DFKI Bremen) \\
 (based on {\sc KnowRob} & (JSK) \\
DY-KNOW & Heitnz, Dowerty \\

@@

>>>>

\begin{tabularx}{\textwidth}{llp{2cm}p{4cm}p{2.3cm}p{2cm}p{2cm}}
\hiderowcolors
{\bf Name} & {\bf Authors (Institution)} & {\bf Surveyed version} & {\bf Project homepage} & {\bf Programming language} & {\bf Knowledge model} & {\bf Reasoner} \\
\hline
\showrowcolors
{\sc KnowRob} & Tenorth (TU Munich) & & & {\sc Prolog} & {\sc Prolog} + OWL-DL & Custom ({\sc Prolog}) \\
ORO & Lemaignan (LAAS-CNRS) & 0.8.0 & \url{oro.openrobots.org} & {\sc Java} & OWL-DL ({\sc Jena}) & {\sc Pellet} \\
PEIS Ecology & Saffiotti (Örebro Univ.) & & \url{www.aass.oru.se/~peis} & {\sc C}\\
 & Kollar, Tellex \\
OMKRF \\
 & Roy, Mavridis \\
 & Wrighteagle \\
 & Vincze \\
 & (Bielfeld) \\
ARMAR & Schmidt-Rohr (Karlsruhe) \\
 & (Saarbrücken) \\
 & Hertzberg (Osnabrück) \\
 & (DFKI Bremen) \\
 (based on {\sc KnowRob} & (JSK) \\
DY-KNOW & Heitnz, Dowerty \\

@@

\subsection{PEIS Ecology}
\label{sect|peis-ecology}

{\sc PEIS Ecology} is a software \emph{ecosystem} that aim to binds autonomous
robotics with ambient intelligence (network of sensors). \emph{PEIS} stands for
\emph{Physically Embedded Intelligent System}: every robots or intelligent
device in the environment is abstracted as a PEIS.

Each PEIS component is running a \emph{PEIS Kernel} instance. Communication between instance rely on a custom P2P communication protocol.

\fixme{Very good website, lot of doc, examples, but could not find something directly related to knowledge representation...}
